`r params$doc_title`

### 2023-04-18 scripts/MSc.Rmd
small changes

---
title: "`r params$doc_title`"
author: | 
        | christoph.reich@med.uni-heidelberg.de 
        | 
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
params:
  date: !r Sys.Date()
  doc_title: "MSc Default Title"
output: 
  html_document:
    code_folding: hide
    theme: paper
    toc: true
    number_sections: true
    toc_float: true
    toc_depth: 4
    df_print: kable
    latex_engine: xelatex
bibliography: ../references/references.bib
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
figurespath <- paste0("../reports/", format(Sys.time(), "%Y%m%d"), '_figures/')
knitr::opts_chunk$set(fig.path = figurespath)  # reference is script! also creates new dirs

@@

library(dplyr)
library(purrr)
library(tidyr)
library(stringr)
library(tibble)
library(ggplot2)
library(ggdist)
library(gghalves)
library(ggthemes)
library(ggpubr)
library(scales)
#library(biomaRt)  # different script
library(kableExtra)
library(MendelianRandomization)
library(TwoSampleMR)
library(mr.raps)
library(MRMix)
library(MRPRESSO)
library(penalized)
# library(rsimsum)   do not use
library(conflicted)
source("helper/MR_lasso.R")  # Slob&Burgess 2020
source("helper/PVE_calculation_fns.R") 
source("helper/plotfigure01fn.R") 
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
# conflict_prefer("kable", "kableExtra")
```

@@

```{r load-data}
my_data <- as_tibble(read.delim("../data-boekstegers_felix/GST_BMI_association_results.txt"))
# GBC: new data 2022-11-04
GBC_dat <- as_tibble(read.delim("../data-boekstegers_felix/C23C24_BMI_association_results.txt"))

# FTO data
FTO_dat <- as_tibble(read.delim("../data-boekstegers_felix/2023-01-19_FTO/FTO_association_results.txt"))
```

@@

```{r highlight-fto-df}
# see script biomart_search.R
rsIds_GeneNames <- as_tibble(readRDS("../data/biomartBMIsearch.rds"))

@@

if (SAVE.files ==TRUE ){
  filenamefig00_b <- paste0("../output/plots/pve/", Sys.Date(), "_explained_var_X_new_sample_size_dep.svg")
  ggsave(filename = filenamefig00_b, plot = fig00_b, 
       width = 10, height = 6, 
       units = "in"  # default
       )
}

@@

# final_plot1.arrange   # OLD
final_plot1.arrange2   # use this!
if (SAVE.files ==TRUE ){
  filename_final_plot1 <- paste0("../output/plots/pve/", Sys.Date(), "_final_plot1.arrange_OLD.svg")
  filename_final_plot1b <- paste0("../output/plots/pve/", Sys.Date(), "_final_plot1b.arrange_NEW.svg")

@@

if (SAVE.files ==TRUE ){
  saveRDS(my_data_harm, paste0("../output/Rdata/", Sys.Date(), "_my_data_harm.rds"))
}

## load results from script `perform_mr.R`
est.bmi.gsd <- readRDS(dplyr::last(list.files("../output/Rdata/", pattern = "_est_BMI_GSD.rds", full.names = TRUE)))

@@

est.bmi.gsd %>% 
  mutate(OR=exp(estimate), CI.lower=exp(estimate-se.estimate),CI.upper=exp(estimate+se.estimate)) %>%  
  kable(digits=3, caption = "MR Results for GSD (outcome) using genetic variants as instrumental variables for BMI") %>% 
  kable_classic(full_width = FALSE, html_font = "Cambria")
```

@@

# SAVE
if (SAVE.files ==TRUE ){
  filename.mr.scatter.gsd <- paste0("../output/plots/mr-analysis/", Sys.Date(), "_figure_mrscatter_gsd.svg")
  ggsave(filename = filename.mr.scatter.gsd, plot = p1.gsd, 
           width = 10, height = 6, 
           units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.forest.gsd <- paste0("../output/plots/mr-analysis/", Sys.Date(), "_figure_mrforest_GSD.svg")
  ggsave(filename = filename.mr.forest.gsd, plot = p2.gsd, 
         width = 5, 
         height = 24, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.funnel.gsd <- paste0("../output/plots/mr-analysis/", Sys.Date(), "_figure_mrfunnel_gsd.svg")
  ggsave(filename = filename.mr.funnel.gsd, plot = p4.gsd, 
         width = 8, 
         height = 4, 
         units = "in"  # default
           )
}

@@

# SAVE
if (SAVE.files ==TRUE ){
  filename.mr.scatter <- paste0("../output/plots/mr-analysis/", Sys.Date(), "_figure_mrscatter.svg")
  ggsave(filename = filename.mr.scatter, plot = p1[[1]], 
           #width = 10, height = 6, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.forest <- paste0("../output/plots/mr-analysis/", Sys.Date(), "_figure_mrforest_GBC.svg")
  ggsave(filename = filename.mr.forest, plot = p2[[1]], 
         width = 5, 
         height = 24, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.funnel.gbc <- paste0("../output/plots/mr-analysis/", Sys.Date(), "_figure_mrfunnel_gbc.svg")
  ggsave(filename = filename.mr.funnel.gbc, plot = p4, 
         width = 8, 
         height = 4, 
         units = "in"  # default
           )
}
```

@@

```{r MendelianRandomization-analysis, warning=FALSE}
## load results
est <- readRDS(file = dplyr::last(list.files("../output/Rdata/", pattern = "_est.rds", full.names = TRUE)))

@@

```{r simulatesimulatesimulate, warning=FALSE}
# save simulation-vars for simulation `simstudy.R` script
sim_vars <- list(n=n, colnames_pval=colnames_pval)
if (SAVE.files ==TRUE ){
  saveRDS(sim_vars, paste0("../output/Rdata/", Sys.Date(), "_sim_vars.rds"))
}
## SIMULATION OUTSOURCED TO "./scripts/simstudy.R"

# read dat from "simstudy.R"  #------------------------------------------------
#est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_NSIM_", full.names = TRUE)))
# from "purrr-simstudy.R"
est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_purrr_NSIM_", full.names = TRUE)))
est_sim_architectures <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_architectures_purrr_NSIM_", full.names = TRUE)))
nsim <- nrow(est_sim)
```

@@

if (SAVE.files ==TRUE ){
  filename_pveplot_sim.raincloud <- paste0("../output/plots/pve/", Sys.Date(), "_figure_simplot_pve_raincloud.svg")
  ggsave(filename = filename_pveplot_sim.raincloud, plot = plot_pve_simulated.raincloud, 
         width = 10, height = 6, 
         units = "in"  # default
         )
}
```

@@

  mutate(across(cols = where(is.numeric), round(3))) %>% 

@@

  # # STORE
  # if (SAVE.files ==TRUE ){
  #   filename.IVW_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_IVW_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = IVW_GSD_performance_metrics, file = filename.IVW_table.performance)
  #   filename.MODE_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_MODE_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = MODE_GSD_performance_metrics, file = filename.MODE_table.performance)
  #   filename.CONMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_CONMIX_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = CONMIX_GSD_performance_metrics, file = filename.CONMIX_table.performance)
  #   filename.MRMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_MRMIX_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = MRMIX_GSD_performance_metrics, file = filename.MRMIX_table.performance)
  #   #5
  #   filename.MEDIAN_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_MEDIAN_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = MEDIAN_GSD_performance_metrics, file = filename.MEDIAN_table.performance)
  #   #6
  #   filename.EGGER_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_EGGER_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = EGGER_GSD_performance_metrics, file = filename.EGGER_table.performance)
  #   #7
  #   filename.ROBUST_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_ROBUST_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = ROBUST_GSD_performance_metrics, file = filename.ROBUST_table.performance)
  #   #8
  #   filename.PRESSO_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_PRESSO_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = PRESSO_GSD_performance_metrics, file = filename.PRESSO_table.performance)
  #   #9
  #   filename.RAPS_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_RAPS_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = RAPS_GSD_performance_metrics, file = filename.RAPS_table.performance)
  #   #10
  #   filename.LASSO_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_LASSO_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = LASSO_GSD_performance_metrics, file = filename.LASSO_table.performance)
  # }

@@

  # ####-------------
  # # SAVE  --------------------------------
  # if (SAVE.files ==TRUE ){
  #   #1
  #   filename_IVW_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_IVW_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_IVW_GSD_simplot_thetas, plot = IVW_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #2
  #   filename_MODE_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MODE_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_MODE_GSD_simplot_thetas, plot = MODE_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #3
  #   filename_CONMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_CONMIX_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_CONMIX_GSD_simplot_thetas, plot = CONMIX_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #4
  #   filename_MRMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MRMIX_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_MRMIX_GSD_simplot_thetas, plot = MRMIX_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #5
  #   filename_MEDIAN_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MEDIAN_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_MEDIAN_GSD_simplot_thetas, plot = MEDIAN_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #6
  #   filename_EGGER_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_EGGER_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_EGGER_GSD_simplot_thetas, plot = EGGER_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #7
  #   filename_ROBUST_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_ROBUST_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_ROBUST_GSD_simplot_thetas, plot = ROBUST_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #8
  #   filename_PRESSO_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_PRESSO_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_PRESSO_GSD_simplot_thetas, plot = PRESSO_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #9
  #   filename_RAPS_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_RAPS_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_RAPS_GSD_simplot_thetas, plot = RAPS_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #10
  #   filename_LASSO_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_LASSO_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_LASSO_GSD_simplot_thetas, plot = LASSO_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  # }

@@

  if (SAVE.files ==TRUE ){
    filename_GSD_simplot_thetas_arrange <- paste0("../output/plots/theta_sims/", Sys.Date(), "_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".svg")
    ggsave(filename = filename_GSD_simplot_thetas_arrange, plot = GSD_simplot_thetas_arrange, 
           width = 10, height = 38, 
           units = "in"  # default
           )
  }

@@

  if (SAVE.files ==TRUE ){
    filename_simplot_bias_mse <- paste0("../output/plots/bias-mse/", Sys.Date(), "_GSD_simplot_bias_mse_REF_METHOD_", selected_true_methods[true_method], "_NSIM_",nsim, ".svg")
    ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot_GSD, 
           width = 7, height = 24, 
           units = "in"  # default
           )
  }
}

@@

    # # STORE
    # if (SAVE.files ==TRUE ){
    #   filename.IVW_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
    #                                       "_IVW_GSD_performance_metrics_TRUE_EST_", 
    #                                       selected_true_methods[true_method], 
    #                                       "_GenArch_", name_GenArch,
    #                                       "_NSIM_", nsim, ".csv")
    #   write.csv2(x = IVW_GSD_performance_metrics, file = filename.IVW_table.performance)
    #   filename.MODE_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
    #                                       "_MODE_GSD_performance_metrics_TRUE_EST_", 
    #                                       selected_true_methods[true_method], 
    #                                       "_GenArch_", name_GenArch,
    #                                       "_NSIM_", nsim, ".csv")
    #   write.csv2(x = MODE_GSD_performance_metrics, file = filename.MODE_table.performance)
    #   filename.CONMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
    #                                       "_CONMIX_GSD_performance_metrics_TRUE_EST_", 
    #                                       selected_true_methods[true_method], 
    #                                       "_GenArch_", name_GenArch,
    #                                       "_NSIM_", nsim, ".csv")
    #   write.csv2(x = CONMIX_GSD_performance_metrics, file = filename.CONMIX_table.performance)
    #   filename.MRMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
    #                                       "_MRMIX_GSD_performance_metrics_TRUE_EST_", 
    #                                       selected_true_methods[true_method], 
    #                                       "_GenArch_", name_GenArch,
    #                                       "_NSIM_", nsim, ".csv")
    #   write.csv2(x = MRMIX_GSD_performance_metrics, file = filename.MRMIX_table.performance)
    #   #5
    #   filename.MEDIAN_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
    #                                       "_MEDIAN_GSD_performance_metrics_TRUE_EST_", 
    #                                       selected_true_methods[true_method], 
    #                                       "_GenArch_", name_GenArch,
    #                                       "_NSIM_", nsim, ".csv")
    #   write.csv2(x = MEDIAN_GSD_performance_metrics, file = filename.MEDIAN_table.performance)
    #   #6
    #   filename.EGGER_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
    #                                       "_EGGER_GSD_performance_metrics_TRUE_EST_", 
    #                                       selected_true_methods[true_method], 
    #                                       "_GenArch_", name_GenArch,
    #                                       "_NSIM_", nsim, ".csv")
    #   write.csv2(x = EGGER_GSD_performance_metrics, file = filename.EGGER_table.performance)
    #   #7
    #   filename.ROBUST_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
    #                                       "_ROBUST_GSD_performance_metrics_TRUE_EST_", 
    #                                       selected_true_methods[true_method], 
    #                                       "_GenArch_", name_GenArch,
    #                                       "_NSIM_", nsim, ".csv")
    #   write.csv2(x = ROBUST_GSD_performance_metrics, file = filename.ROBUST_table.performance)
    #   #8
    #   filename.PRESSO_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
    #                                       "_PRESSO_GSD_performance_metrics_TRUE_EST_", 
    #                                       selected_true_methods[true_method], 
    #                                       "_GenArch_", name_GenArch,
    #                                       "_NSIM_", nsim, ".csv")
    #   write.csv2(x = PRESSO_GSD_performance_metrics, file = filename.PRESSO_table.performance)
    #   #9
    #   filename.RAPS_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
    #                                       "_RAPS_GSD_performance_metrics_TRUE_EST_", 
    #                                       selected_true_methods[true_method], 
    #                                       "_GenArch_", name_GenArch,
    #                                       "_NSIM_", nsim, ".csv")
    #   write.csv2(x = RAPS_GSD_performance_metrics, file = filename.RAPS_table.performance)
    #   #10
    #   filename.LASSO_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
    #                                       "_LASSO_GSD_performance_metrics_TRUE_EST_", 
    #                                       selected_true_methods[true_method], 
    #                                       "_GenArch_", name_GenArch,
    #                                       "_NSIM_", nsim, ".csv")
    #   write.csv2(x = LASSO_GSD_performance_metrics, file = filename.LASSO_table.performance)
    # }

@@

    ####-------------
    # SAVE  --------------------------------
    # #1
    # filename_IVW_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_IVW_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], 
    #                                           "_GenArch_", name_GenArch, "_NSIM_", nsim,".png")
    # ggsave(filename = filename_IVW_GSD_simplot_thetas, plot = IVW_GSD_simplot_thetas, 
    #        width = 15, height = 6, 
    #        units = "in"  # default
    #        )
    # #2
    # filename_MODE_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MODE_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], 
    #                                            "_GenArch_", name_GenArch, "_NSIM_", nsim,".png")
    # ggsave(filename = filename_MODE_GSD_simplot_thetas, plot = MODE_GSD_simplot_thetas, 
    #        width = 15, height = 6, 
    #        units = "in"  # default
    #        )
    # #3
    # filename_CONMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_CONMIX_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], 
    #                                              "_GenArch_", name_GenArch, "_NSIM_", nsim,".png")
    # ggsave(filename = filename_CONMIX_GSD_simplot_thetas, plot = CONMIX_GSD_simplot_thetas, 
    #        width = 15, height = 6, 
    #        units = "in"  # default
    #        )
    # #4
    # filename_MRMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MRMIX_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], 
    #                                             "_GenArch_", name_GenArch, "_NSIM_", nsim,".png")
    # ggsave(filename = filename_MRMIX_GSD_simplot_thetas, plot = MRMIX_GSD_simplot_thetas, 
    #        width = 15, height = 6, 
    #        units = "in"  # default
    #        )
    # #5
    # filename_MEDIAN_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MEDIAN_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], 
    #                                              "_GenArch_", name_GenArch, "_NSIM_", nsim,".png")
    # ggsave(filename = filename_MEDIAN_GSD_simplot_thetas, plot = MEDIAN_GSD_simplot_thetas, 
    #        width = 15, height = 6, 
    #        units = "in"  # default
    #        )
    # #6
    # filename_EGGER_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_EGGER_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], 
    #                                             "_GenArch_", name_GenArch, "_NSIM_", nsim,".png")
    # ggsave(filename = filename_EGGER_GSD_simplot_thetas, plot = EGGER_GSD_simplot_thetas, 
    #        width = 15, height = 6, 
    #        units = "in"  # default
    #        )
    # #7
    # filename_ROBUST_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_ROBUST_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method],
    #                                              "_GenArch_", name_GenArch, "_NSIM_", nsim,".png")
    # ggsave(filename = filename_ROBUST_GSD_simplot_thetas, plot = ROBUST_GSD_simplot_thetas, 
    #        width = 15, height = 6, 
    #        units = "in"  # default
    #        )
    # #8
    # filename_PRESSO_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_PRESSO_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method],
    #                                              "_GenArch_", name_GenArch, "_NSIM_", nsim,".png")

>>>>

---
title: "`r params$doc_title`"
author: | 
        | christoph.reich@med.uni-heidelberg.de 
        | 
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
params:
  date: !r Sys.Date()
  doc_title: "MSc Default Title"
output: 
  html_document:
    code_folding: hide
    theme: paper
    toc: true
    number_sections: true
    toc_float: true
    toc_depth: 4
    df_print: kable
    latex_engine: xelatex
bibliography: ./references/references.bib
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
figurespath <- paste0("./reports/", format(Sys.time(), "%Y%m%d"), '_figures/')
knitr::opts_chunk$set(fig.path = figurespath)  # reference is script! also creates new dirs

@@

library(dplyr)
library(purrr)
library(tidyr)
library(stringr)
library(tibble)
library(ggplot2)
library(ggdist)
library(gghalves)
library(ggthemes)
library(ggpubr)
library(gt)
library(scales)
#library(biomaRt)  # different script
library(kableExtra)
library(MendelianRandomization)
library(TwoSampleMR)
library(mr.raps)
library(MRMix)
library(MRPRESSO)
library(penalized)
# library(rsimsum)   do not use
library(conflicted)
source("helper/MR_lasso.R")  # Slob&Burgess 2020
source("helper/PVE_calculation_fns.R") 
source("helper/plotfigure01fn.R") 
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflicts_prefer(kableExtra::kable)
# conflict_prefer("kable", "kableExtra")
```

@@

```{r load-data}
my_data <- as_tibble(read.delim("./data-boekstegers_felix/GST_BMI_association_results.txt"))
# GBC: new data 2022-11-04
GBC_dat <- as_tibble(read.delim("./data-boekstegers_felix/C23C24_BMI_association_results.txt"))

# FTO data
FTO_dat <- as_tibble(read.delim("./data-boekstegers_felix/2023-01-19_FTO/FTO_association_results.txt"))
```

@@

```{r highlight-fto-df}
# see script biomart_search.R
rsIds_GeneNames <- as_tibble(readRDS("./data/biomartBMIsearch.rds"))

@@

if (SAVE.files ==TRUE ){
  filenamefig00_b <- paste0("./output/plots/pve/", Sys.Date(), "_explained_var_X_new_sample_size_dep.svg")
  ggsave(filename = filenamefig00_b, plot = fig00_b, 
       width = 10, height = 6, 
       units = "in"  # default
       )
}

@@

# final_plot1.arrange   # OLD
final_plot1.arrange2   # use this!
if (SAVE.files ==TRUE ){
  filename_final_plot1 <- paste0("./output/plots/pve/", Sys.Date(), "_final_plot1.arrange_OLD.svg")
  filename_final_plot1b <- paste0("./output/plots/pve/", Sys.Date(), "_final_plot1b.arrange_NEW.svg")

@@

if (SAVE.files ==TRUE ){
  saveRDS(my_data_harm, paste0("./output/Rdata/harmonized-dat/", Sys.Date(), "_my_data_harm.rds"))
}

## load results from script `perform_mr.R`
est.bmi.gsd <- readRDS(dplyr::last(list.files("./output/Rdata/mr-results/", pattern = "_est_BMI_GSD.rds", full.names = TRUE)))

@@

est.bmi.gsd %>% 
  mutate(OR=exp(estimate), CI.lower=exp(estimate-se.estimate),CI.upper=exp(estimate+se.estimate)) %>%  
  mutate(across(where(is.numeric), round, 3)) %>% 
  arrange(tolower(mr_methods)) %>% 
  relocate(time, .after = last_col()) -> est.bmi.gsd.table

# est.bmi.gsd.table %>% 
#   kable(digits=3, caption = "MR Results for GSD (outcome) using genetic variants as instrumental variables for BMI") %>% 
#   kable_classic(full_width = FALSE, html_font = "Cambria")

est.bmi.gsd.table %>% 
  gt() %>% 
  cols_merge(
      columns = c(estimate, se.estimate),
      pattern = "{1} [\u00b1 {2}]"  # +- sign : "\u00b1"
    ) %>% 
  cols_merge(
      columns = c(OR, CI.lower, CI.upper),
      pattern = "{1} [{2}; {3}]"  
    ) %>% 
  cols_label(
    mr_methods = md("Methods"),
    estimate = md("Estimate [\u00b1 StdErr]"),
    OR = md("OR [95% CI]"),
    time=md("Computational time [sec]")
  ) %>% 
  fmt_number(decimals = 3, use_seps=TRUE) %>% 
  tab_source_note(
    source_note = md("MR Results for GSD (outcome) using genetic variants as instrumental variables for BMI")
  ) %>% 
  opt_stylize(style=1, color="gray") -> gt.tables.est.bmi.gsd

if (SAVE.files ==TRUE ){
 filename.gt.est.bmi.gsd <- paste0("./output/gt-tables/mr-estimates/", Sys.Date(), 
                                       "_est_bmi_gsd")

 gt.tables.est.bmi.gsd %>% 
   gtsave(paste0(filename.gt.est.bmi.gsd, ".docx"))   # alternative .rtf, .tex, .png, .html
 gt.tables.est.bmi.gsd %>% 
   gtsave(paste0(filename.gt.est.bmi.gsd, ".html")) 
}
```

@@

# SAVE
if (SAVE.files ==TRUE ){
  filename.mr.scatter.gsd <- paste0("./output/plots/mr-analysis/", Sys.Date(), "_figure_mrscatter_gsd.svg")
  ggsave(filename = filename.mr.scatter.gsd, plot = p1.gsd, 
           width = 10, height = 6, 
           units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.forest.gsd <- paste0("./output/plots/mr-analysis/", Sys.Date(), "_figure_mrforest_GSD.svg")
  ggsave(filename = filename.mr.forest.gsd, plot = p2.gsd, 
         width = 5, 
         height = 24, 
           #units = "in"  # default
           )
}
```

@@

ggarrange(p1.gsd, p4.gsd, nrow = 1, labels = c("A", "B")) -> gsd_scatter_funnel_arrange

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.funnel.gsd <- paste0("./output/plots/mr-analysis/", Sys.Date(), "_figure_mrfunnel_gsd.svg")
  filename.mr.scatterfunnel.gsd <- paste0("./output/plots/mr-analysis/", Sys.Date(), "_figure_scatter_mrfunnel_arrange_gsd.svg")
  ggsave(filename = filename.mr.funnel.gsd, plot = p4.gsd, 
         width = 8, 
         height = 4, 
         units = "in"  # default
           )

  ggsave(filename.mr.scatterfunnel.gsd, gsd_scatter_funnel_arrange, width=8, height=4, units="in")
}

@@

# SAVE
if (SAVE.files ==TRUE ){
  filename.mr.scatter <- paste0("./output/plots/mr-analysis/", Sys.Date(), "_figure_mrscatter.svg")
  ggsave(filename = filename.mr.scatter, plot = p1[[1]], 
           #width = 10, height = 6, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.forest <- paste0("./output/plots/mr-analysis/", Sys.Date(), "_figure_mrforest_GBC.svg")
  ggsave(filename = filename.mr.forest, plot = p2[[1]], 
         width = 5, 
         height = 24, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.funnel.gbc <- paste0("./output/plots/mr-analysis/", Sys.Date(), "_figure_mrfunnel_gbc.svg")
  ggsave(filename = filename.mr.funnel.gbc, plot = p4, 
         width = 8, 
         height = 4, 
         units = "in"  # default
           )
}
```

@@

```{r MendelianRandomization-analysis, warning=FALSE}
## load results
est <- readRDS(file = dplyr::last(list.files("./output/Rdata/mr-results/", pattern = "_est.rds", full.names = TRUE)))

@@

```{r simulatesimulatesimulate, warning=FALSE}
# save simulation-vars for simulation `simstudy.R` script
sim_vars <- list(n=n, colnames_pval=colnames_pval)
if (SAVE.files ==TRUE ){
  saveRDS(sim_vars, paste0("./output/Rdata/", Sys.Date(), "_sim_vars.rds"))
}
## SIMULATION OUTSOURCED TO "./scripts/simstudy.R"

# read dat from "simstudy.R"  #------------------------------------------------
#est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_NSIM_", full.names = TRUE)))
# from "purrr-simstudy.R"
est_sim <- readRDS(dplyr::last(list.files(path = "./output/Rdata/sim-results/", pattern = "_est_sim_purrr_NSIM_", full.names = TRUE)))
est_sim_architectures <- readRDS(dplyr::last(list.files(path = "./output/Rdata/sim-results/", pattern = "_est_sim_architectures_purrr_NSIM_", full.names = TRUE)))
nsim <- nrow(est_sim)
nsim_architectures <- nrow(est_sim_architectures[[1]])
```

@@

if (SAVE.files ==TRUE ){
  filename_pveplot_sim.raincloud <- paste0("./output/plots/pve/", Sys.Date(), "_figure_simplot_pve_raincloud.svg")
  ggsave(filename = filename_pveplot_sim.raincloud, plot = plot_pve_simulated.raincloud, 
         width = 10, height = 6, 
         units = "in"  # default
         )
}
```

@@

  mutate(across(where(is.numeric), round, 3)) %>% 

@@

@@

@@

  if (SAVE.files ==TRUE ){
    filename_GSD_simplot_thetas_arrange <- paste0("./output/plots/theta_sims/", Sys.Date(), "_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".svg")
    ggsave(filename = filename_GSD_simplot_thetas_arrange, plot = GSD_simplot_thetas_arrange, 
           width = 10, height = 38, device = "svg",
           units = "in"  # default
           )
  }

@@

  if (SAVE.files ==TRUE ){
    filename_simplot_bias_mse <- paste0("./output/plots/bias-mse/", Sys.Date(), "_GSD_simplot_bias_mse_REF_METHOD_", selected_true_methods[true_method], "_NSIM_",nsim, ".svg")
    ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot_GSD, 
           width = 7, height = 24, 
           units = "in"  # default
           )
  }
}

@@

@@
